Latent Variable Clustering for Classification of Events in the AT-TPC

### 2020-06-07 doc/Manuscript/article.tex
Updates from Overleaf

\noindent Since there are then only three remaining hyperparameters we choose to perform a coarse grid-search as described in section \ref{sec:hyperparam_search_arch}.

@@

To train the MIXAE clustering algorithm, we use the large simulated dataset with $M=80000$ points, evenly distributed between proton- and carbon-events. The algorithm is trained on a subset of $60000$ of these samples, and we track performance on the remaining $20000$ events.

@@

We repeat the optimization steps in the previous section for the filtered AT-TPC data. The exception being that we allow the algorithm to train on the labelled samples. Beginning with a wide grid equal to the grid used for the simulated data we searched over all parameter configurations to find promising values. We then performed a local search around these values to pin-point the hyperparameter configuration. This search yielded the optimal hyper-parameters

@@

As in the two previous sections, we repeat the same procedure of iterative grid searches on the MIXAE loss-weights. Each configuration is re-run a total of $N=10$ times to capture fluctuations in the performance before a final selection is made on the hyperparameters. For the full dataset the MIXAE hyperparameters converge to the same values as for the clean data, i.e.

@@

>>>>

@@

@@

We repeat the optimization steps in the previous section for the filtered AT-TPC data. The exception being that we allow the algorithm to train on the labelled samples. Beginning with a wide grid equal to the grid used for the simulated data we searched over all parameter configurations to find promising values. We then performed a local search around these values to pin-point the hyperparameter configuration.

@@

As in the two previous sections, we repeat the same procedure of iterative grid searches on the MIXAE loss-weights. Each configuration is re-run a total of $N=10$ times to capture fluctuations in the performance before a final selection is made on the hyperparameters.

@@

\section{MIXAE hyper-parameter tuning}

To train the MIXAE clustering algorithm, we use the large simulated dataset with $M=80000$ points, evenly distributed between proton- and carbon-events. The algorithm is trained on a subset of $60000$ of these samples, and we track performance on the remaining $20000$ events. Since there are then only three remaining hyperparameters we choose to perform a coarse grid-search as described in section \ref{sec:hyperparam_search_arch}.

For the full dataset the MIXAE hyperparameters converge to the same values as for the clean data:

Lastly we supply the configuration used for the individual convolutional autoencoder networks in table \ref{tab:mixe_ae_hyperparams}
